My title

### 2024-03-14 paper/paper.qmd
More models and changes to the cleaning

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  #statistic = "mad",
  fmt = 2
)

@@

# Discussion

@@

pp_check(p_average_model) +
  theme(legend.position = "bottom")

# Create the posterior predictive check plot with the specified theme
pp_plot <- pp_check(p_average_model, theme = theme_classic()) +
  theme(legend.position = "bottom")

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
library(modelsummary)
modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  #statistic = "mad",
  fmt = 2
)

@@

library(rstanarm)
library(here)
library(ggplot2)
library(modelsummary)

# Assuming you've already read your models as before
neg_binom_model <- readRDS(file = here::here("models/neg_binom_model.rds"))
stan_neg_binom_model <- readRDS(file = here::here("models/stan_neg_binom_model.rds"))
stan_poisson_model <-readRDS(file = here::here("models/stan_poisson_model.rds"))
first_model <-
  readRDS(file = here::here("models/first_model.rds"))

if (!requireNamespace("broom.mixed", quietly = TRUE)) {
  install.packages("broom.mixed")
}

library(broom.mixed)

# Summarize the models
modelsummary(
  list(
    "Poisson" = cause_of_death_alberta_poisson,
    "Negative binomial" = cause_of_death_alberta_neg_binomial
  ),
  coef_map = coef_short_names,
  estimate_function = function(model) {
    broom.mixed::tidy(model, parameters = "all", conf.int = TRUE)
  }
)

pp_check(first_model) +
  theme(legend.position = "bottom")

pp_check(poisson_model) +
  theme(legend.position = "bottom")

pp_stan_neg_binom_model <- pp_check(stan_neg_binom_model)
pp_stan_neg_binom_model + theme(legend.position = "bottom")

pp_stan_poisson_model <- pp_check(stan_poisson_model)
pp_stan_poisson_model + theme(legend.position = "bottom")

```
# Discussion

@@

# library(bayesplot)
# 
# ppc <- pp_check(p_average_model, type = "dens_overlay")
# 
# # Add a classic theme to the plot
# #ppc + theme_classic()
# 
# # Print the plot
# print(ppc)
# Create the posterior predictive check plot with the specified theme
pp_plot <- pp_check(p_average_model, theme = theme_classic()) +
  theme(legend.position = "bottom")
